Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-05-05 Supplemental-Material-A-Annotated-Analysis.Rmd
student means added + varNam fixes

---
title: "Supplemental Information A: Full Annotated Analysis and Reproducible Code"
subtitle: "Supplemental Material for 'Qualitative Goals'"
author:
- ██████ ██████████^1^
- ██████████ ████████^1^
- █████ █████████^1^
- █████ ██ █████^1^
- ███ ███████^1^
- ^1^██████████ ██ █████████, Department of Psychology
- "Author Information:"
- "Correspondence concerning this article should be addressed to ██████ ██████████, ██████████ ██ ██████████, █████████ ██ ██████████, █████ ██████████ ███, ████ ██ █████████ ████████████████. E-mail: █████████████████"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970" target="_blank">osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://github.com/maskedForPeerReview" target="_blank">github.com/maskedForPeerReview</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
#bibliography: references.bib
csl: apa.csl
header-includes:
   - \usepackage{amsmath, nccmath}
---

@@

# Load Custom Packages
source("./scripts/functions/fun.panel.R")
source("./scripts/functions/themes.R")
source("./scripts/functions/binaryCor.R")
source("./scripts/functions/MlCorMat.R")
source("./scripts/functions/MlTbl.R")
source("./scripts/functions/metaLmer.R")

@@

# -------------------------------------------------------------------------------------------------------------
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
pairs.panels.new(
  df[c("RelatednessSelf", "RelatednessOther")],
  labels = c(
    "I shared information about myself.",
    "X shared information about themselves."
  )
)
df$RelatednessInteraction <-
  rowMeans(df[c("RelatednessSelf", "RelatednessOther")], na.rm = T)
df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <-
  NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
df$Relatedness <-
  rowMeans(df[, c("RelatednessInteraction", "RelatednessNoInteraction")],
    na.rm =
      T
  )
# Pro-Sociality
df$ProSo <-
  rowMeans(df[, c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm = T)
# Anti-Sociality
df$AntiSo <-
  rowMeans(df[, c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm = T)

@@

# -------------------------------------------------------------------------------------------------------------
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
pairs.panels.new(
  df[c("RelatednessSelf", "RelatednessOther")],
  labels = c(
    "I shared information about myself.",
    "X shared information about themselves."
  )
)
df$RelatednessInteraction <-
  rowMeans(df[c("RelatednessSelf", "RelatednessOther")], na.rm = T)
df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <-
  NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
df$Relatedness <-
  rowMeans(df[, c("RelatednessInteraction", "RelatednessNoInteraction")],
           na.rm = TRUE) %>%
  ifelse(is.nan(.), NA, .)

@@

@@

```{r studentDataSelection}

@@

@@

```{r medicalDataSelection}
varListMedical <- 
  c(
    # "KeyNeedFulfillment",
    # "KeyNeedImp",
    "DaytimeNeedFullfillment",
    "DaytimeNeedImportance",
    "InteractionNeedFullfillment",
    "InteractionNeedImportance",
    "AntiSo1",
    "AntiSo2",
    "AntiSo3",
    "AntiSo4",
    "AntiSo5",
    "AntiSo6",
    "AntiSo7",
    "ProSo1",
    "ProSo2",
    "ProSo3",
    "ProSo4",
    "StudentGoal01",
    "StudentGoal02",
    "StudentGoal03",
    "StudentGoal04",
    "StudentGoal05",
    "StudentGoal06",
    "StudentGoal07",
    "StudentGoal08",
    "StudentGoal09",
    "StudentGoal10",
    "Autonomy",
    "Competence",
    # Break relatedness up into interaction vs. no interaction(?)
    # vars are already calculated
    "Relatedness",
    "AttitudesDutch",
    "AttitudesPartner",
    "exWB",
    "angry",
    "afraid",
    "energy",
    "lonelyAlways",
    "Event"
  )

varNameListMedical <- 
  c(
    # "KeyNeedFulfillment" = "Key Need Fulfillment",
    # "KeyNeedImp" = "Key Need Importance",
    "DaytimeNeedFullfillment" = "Daytime Core Motive Fulfillment",
    "DaytimeNeedImportance" = "Daytime Core Motive Importance",
    "InteractionNeedFullfillment" = "Interaction Core Motive Fulfillment",
    "InteractionNeedImportance" = "Interaction Core Motive Importance",
    "AntiSo1" = "Put someone down",
    "AntiSo2" = "Show little attention in someones opinion",
    "AntiSo3" = "Demeaning remarks",
    "AntiSo4" = "Inpropperly addressing someone",
    "AntiSo5" = "Ignored or excluded someone",
    "AntiSo6" = "Doubt someones judgement",
    "AntiSo7" = "Unwanted attempts of personal matters",
    "ProSo1" = "Listen to someones problems",
    "ProSo2" = "Cheer someone up",
    "ProSo3" = "Help someone get things done",
    "ProSo4" = "Help someone with responsibilities",
    "StudentGoal01" = "Social support and connectedness",
    "StudentGoal02" = "Romantic or sexual relationship",
    "StudentGoal03" = "Academic",
    "StudentGoal04" = "Career",
    "StudentGoal05" = "Financial",
    "StudentGoal06" = "Health and fitness",
    "StudentGoal07" = "Leasure and fun",
    "StudentGoal08" = "Personal improvement and growth",
    "StudentGoal09" = "Service and help",
    "StudentGoal10" = "Spiritual or religious",
    "Autonomy" = "Autonomy",
    "Competence" = "Competence",
    # Break relatedness up into interaction vs. no interaction(?)
    # vars are already calculated
    "Relatedness" = "Relatedness",
    "AttitudesDutch" = "Outgroup Attitude",
    "AttitudesPartner" = "Attitude Interaction Partner",
    "exWB" = "Sadness Happiness",
    "angry" = "Anger",
    "afraid" = "Anxiety",
    "energy" = "Energy",
    "lonelyAlways" = "Loneliness",
    "Event" = "Positive or negative event present"
  )

@@

dtMedical$vizall <- dtMedical$full %>%
  select(
    PID,
    TID,
    TIDnum,
    varListMedical
  )

dtMedical$viz$DaytimeNeed <- dtMedical$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    starts_with("DaytimeNeed")
  )

dtMedical$viz$InteractionNeed <- dtMedical$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    starts_with("InteractionNeed")
  )

@@

lWideToLong <- function(data, ...){
  reshape2::melt(
    data, 
    id.vars = c("PID", "TIDnum")
  )
}

dtMedical$vizLong <- lapply(
  dtMedical$viz,
  lWideToLong
)

@@

```{r MeanVizFun}

lWideToLong <- function(data, ...){
  reshape2::melt(
    data, 
    id.vars = c("PID", "TID", "TIDnum")
  )
}

meanVarPlot <- function(dataIn, name, namList,...){
  # dataIn <- dtMedical$viz$InteractionNeed
  # name <- "Interaction Core Need"
  # namList <- varNameListMedical
  dataLong <- dataIn %>%
    mutate(TID = stri_replace_all_regex(
      TID,
      pattern = c('Morning', 'Afternoon'),
      replacement = c('12:00:00', '19:00:00'),
      vectorize = FALSE
    ) %>% as.POSIXct) %>%
    lWideToLong %>%
    mutate(variable = recode(variable, !!!namList))

  pTidMain <-
    ggplot(dataLong,
           aes(x = TIDnum, y = value, color = variable)) +
    geom_point(alpha = 0) +
    stat_summary(fun = mean, geom = "line") +
    labs(y = "Mean per Day",
         x = "Time Index") +
    #scale_colour_manual(values = RColorBrewer::brewer.pal(length(unique(dataLong$variable)), "Set3")) +
    ggthemes::scale_colour_calc() +
    scale_x_continuous(breaks = seq(0, max(dataLong$TIDnum), 25)) +
    theme_Publication() +
    theme(
      panel.border = element_rect(colour = "black"),
      plot.margin = margin(0, 10, 10, 10, "mm")
    )
  pTidTop <-
    ggplot(dataLong %>% filter(!is.na(value)), aes(x = TIDnum, y = (..count.. / max(count)) * 100),
           color = variable) +
    geom_freqpoly(binwidth = 2) +
    geom_hline(yintercept = 80,
               linetype = "dashed",
               color = "black") +
    annotate(
      # add white background
      "label",
      x = max(dataLong$TIDnum),
      y = 80,
      label = "80%",
      vjust = 0.5,
      hjust = -1,
      label.size = NA
    )  +
    coord_cartesian(clip = "off") +
    labs(y = "Percentage") +
    #scale_colour_manual(values = rep("black", 20)) +
    theme_classic() +
    theme(
      legend.position = "none",
      axis.line.x = element_blank(),
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      plot.margin = margin(0, 10, 0, 10, "mm")
    )

  pTidTitle <- cowplot::ggdraw() +
    cowplot::draw_label(
      paste("Variable Set:", name, "[Time Id Plot]"),
      fontface = 'bold',
      x = 0.5,
      hjust = 0.5
    )

  pTid <- cowplot::plot_grid(
    pTidTitle,
    pTidTop,
    pTidMain,
    align = "v",
    nrow = 3,
    rel_heights = c(0.1, 1 / 5, 4 / 5)
  )

  pDateMain <-
    ggplot(dataLong,
           aes(x = TID, y = value, color = variable)) +
    geom_point(alpha = 0) +
    stat_summary(fun = mean, geom = "line") +
    labs(y = "Mean per Day",
         x = "Date") +
    #scale_colour_manual(values = RColorBrewer::brewer.pal(length(unique(dataLong$variable)), "Set3")) +
    ggthemes::scale_colour_calc() +
    scale_x_datetime(breaks = scales::date_breaks("10 day")) +
    theme_Publication() +
    theme(
      panel.border = element_rect(colour = "black"),
      plot.margin = margin(0, 10, 10, 10, "mm")
    )
  pDateTop <-
    ggplot(dataLong,
           aes(
             x = TID,
             y = (..count.. / max(count)) * 100,
             color = variable
           )) +
    geom_freqpoly(binwidth = 1 * 3600 * 24) +
    geom_hline(yintercept = 80,
               linetype = "dashed",
               color = "black") +
    annotate(
      # add white background
      "label",
      x = max(unique(dataLong$TID)),
      y = 80,
      label = "80%",
      vjust = 0.5,
      hjust = -1,
      label.size = NA
    )  +
    coord_cartesian(clip = "off") +
    labs(y = "Percentage") +
    scale_colour_manual(values = rep("black", 20)) +
    theme_classic() +
    theme(
      legend.position = "none",
      axis.line.x = element_blank(),
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      plot.margin = margin(0, 10, 0, 10, "mm")
    )

  pDateTitle <- cowplot::ggdraw() +
    cowplot::draw_label(
      paste("Variable Set: Key-Need", "[Date Plot]"),
      fontface = 'bold',
      x = 0.5,
      hjust = 0.5
    )

  pDate <- cowplot::plot_grid(
    pDateTitle,
    pDateTop,
    pDateMain,
    align = "v",
    nrow = 3,
    rel_heights = c(0.1, 1 / 5, 4 / 5)
  )

  list(pTid, pDate)
  pTid
}
```

```{r medicalMeanViz, echo=FALSE, results='hide',fig.keep='all'} 
#, warning=FALSE, message=FALSE, error=FALSE
# meanVarPlot(dtMedical$viz$DaytimeNeed, "Key-Need")
# meanVarPlot(dtMedical$viz$AntiSocialBehavior, "Anti-Social Behavior")

dtMedical$vizPlots <-
  lapply(seq_along(dtMedical$viz),
         function(i)
           meanVarPlot(dataIn = dtMedical$viz[[i]], 
                       name = names(dtMedical$viz)[[i]], 
                       namList = varNameListMedical))
dtMedical$vizPlots
```

>>>>

---
title: "Supplemental Information A: Full Annotated Analysis and Reproducible Code"
subtitle: "Supplemental Material for 'Qualitative Goals'"
author:
- ██████ ██████████^1^
- ██████████ ████████^1^
- █████ █████████^1^
- █████ ██ █████^1^
- ███ ███████^1^
- ^1^██████████ ██ █████████, Department of Psychology
- "Author Information:"
- "Correspondence concerning this article should be addressed to ██████ ██████████, ██████████ ██ ██████████, █████████ ██ ██████████, █████ ██████████ ███, ████ ██ █████████ ████████████████. E-mail: █████████████████"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io/TBD" target="_blank">osf.io/TBD</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://github.com/maskedForPeerReview" target="_blank">github.com/maskedForPeerReview</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
#bibliography: references.bib
csl: apa.csl
header-includes:
   - \usepackage{amsmath, nccmath}
---

@@

# Load Custom Packages
source("./scripts/functions/fun.panel.R")
source("./scripts/functions/themes.R")
source("./scripts/functions/binaryCor.R")
source("./scripts/functions/MlCorMat.R")
source("./scripts/functions/MlTbl.R")
source("./scripts/functions/metaLmer.R")
source("./scripts/functions/meanViz.R")

@@

df$IntergroupContact <- (df$IntergroupContact-2)*-1

# Fix naming issues
df$AttitudesPartner <- df$AttitdutuesPartnerstick

# -------------------------------------------------------------------------------------------------------------
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
pairs.panels.new(
  df[c("RelatednessSelf", "RelatednessOther")],
  labels = c(
    "I shared information about myself.",
    "X shared information about themselves."
  )
)
df$RelatednessInteraction <- rowMeans(df[c("RelatednessSelf", "RelatednessOther")], na.rm = TRUE)
df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <- NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
df$Relatedness <-
  rowMeans(df[, c("RelatednessInteraction", "RelatednessNoInteraction")],
           na.rm = TRUE) %>%
  ifelse(is.nan(.), NA, .)

# Core Need
df$DaytimeNeedFullfillment[df$InteractionDum == 0 & !is.na(df$KeyNeedFullfillment)] <-
  df$KeyNeedFullfillment[df$InteractionDum == 0 & !is.na(df$KeyNeedFullfillment)]

df$InteractionNeedFullfillment <- NA 
df$InteractionNeedFullfillment[df$InteractionDum == 1 & !is.na(df$KeyNeedFullfillment)] <- 
  df$KeyNeedFullfillment[df$InteractionDum == 1 & !is.na(df$KeyNeedFullfillment)]

@@

df$IntergroupContact <- (df$IntergroupContact-2)*-1

# -------------------------------------------------------------------------------------------------------------
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
pairs.panels.new(
  df[c("RelatednessSelf", "RelatednessOther")],
  labels = c(
    "I shared information about myself.",
    "X shared information about themselves."
  )
)
df$RelatednessInteraction <-
  rowMeans(df[c("RelatednessSelf", "RelatednessOther")], na.rm = TRUE)
df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <- NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
df$Relatedness <-
  rowMeans(df[, c("RelatednessInteraction", "RelatednessNoInteraction")],
           na.rm = TRUE) %>%
  ifelse(is.nan(.), NA, .)

@@

# Pro-Sociality
df$ProSo <-
  rowMeans(df[, c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm = TRUE)
# Anti-Sociality
df$AntiSo <-
  rowMeans(df[, c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm = TRUE)

@@

```{r studentDataSelection}
varListStudent <- 
  c(
    "IntergroupContact",
    "InteractionDum",
    # "KeyNeedFullfillment",
    # "KeyNeedImp",
    "DaytimeNeedFullfillment",
    #"DaytimeNeedImportance",
    "InteractionNeedFullfillment",
    #"InteractionNeedImportance",
    "AntiSo1",
    "AntiSo2",
    "AntiSo3",
    "AntiSo4",
    "AntiSo5",
    "AntiSo6",
    "AntiSo7",
    "ProSo1",
    "ProSo2",
    "ProSo3",
    "ProSo4",
    "StudentGoal01",
    "StudentGoal02",
    "StudentGoal03",
    "StudentGoal04",
    "StudentGoal05",
    "StudentGoal06",
    "StudentGoal07",
    "StudentGoal08",
    "StudentGoal09",
    "StudentGoal10",
    "Autonomy",
    "Competence",
    # Break relatedness up into interaction vs. no interaction(?)
    # vars are already calculated
    "Relatedness",
    "AttitudesDutch",
    "AttitudesPartner",
    "ExWB",
    #"angry",
    #"afraid",
    #"energy",
    #"lonelyAlways",
    "Event"
  )

varNameListStudent <- 
  c(
    "IntergroupContact" = "Dutch Interaction",
    "InteractionDum" = "Any Interaction",
    # "KeyNeedFulfillment" = "Key Need Fulfillment",
    # "KeyNeedImp" = "Key Need Importance",
    "DaytimeNeedFullfillment" = "Daytime Core Motive Fulfillment",
    #"DaytimeNeedImportance" = "Daytime Core Motive Importance",
    "InteractionNeedFullfillment" = "Interaction Core Motive Fulfillment",
    #"InteractionNeedImportance" = "Interaction Core Motive Importance",
    "AntiSo1" = "Put someone down",
    "AntiSo2" = "Show little attention in someones opinion",
    "AntiSo3" = "Demeaning remarks",
    "AntiSo4" = "Inpropperly addressing someone",
    "AntiSo5" = "Ignored or excluded someone",
    "AntiSo6" = "Doubt someones judgement",
    "AntiSo7" = "Unwanted attempts of personal matters",
    "ProSo1" = "Listen to someones problems",
    "ProSo2" = "Cheer someone up",
    "ProSo3" = "Help someone get things done",
    "ProSo4" = "Help someone with responsibilities",
    "StudentGoal01" = "Social support and connectedness",
    "StudentGoal02" = "Romantic or sexual relationship",
    "StudentGoal03" = "Academic",
    "StudentGoal04" = "Career",
    "StudentGoal05" = "Financial",
    "StudentGoal06" = "Health and fitness",
    "StudentGoal07" = "Leasure and fun",
    "StudentGoal08" = "Personal improvement and growth",
    "StudentGoal09" = "Service and help",
    "StudentGoal10" = "Spiritual or religious",
    "Autonomy" = "Autonomy",
    "Competence" = "Competence",
    # Break relatedness up into interaction vs. no interaction(?)
    # vars are already calculated
    "Relatedness" = "Relatedness",
    "AttitudesDutch" = "Outgroup Attitude",
    "AttitudesPartner" = "Attitude Interaction Partner",
    "ExWB" = "Sadness Happiness",
    #"angry" = "Anger",
    #"afraid" = "Anxiety",
    #"energy" = "Energy",
    #"lonelyAlways" = "Loneliness",
    "Event" = "Positive or negative event present"
  )

dtStudents$viz <- list()

dtStudents$vizall <- dtStudents$full %>%
  select(
    PID,
    TID,
    TIDnum,
    all_of(varListStudent)
  )

dtStudents$viz$Interaction <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    IntergroupContact,
    InteractionDum
  )

dtStudents$viz$KeyNeed <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    DaytimeNeedFullfillment,
    InteractionNeedFullfillment
  )

dtStudents$viz$AntiSocialBehaviorPt1 <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    AntiSo1,
    AntiSo2,
    AntiSo3
  )

dtStudents$viz$AntiSocialBehaviorPt2 <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    AntiSo4,
    AntiSo5
  )

dtStudents$viz$AntiSocialBehaviorPt3 <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    AntiSo6,
    AntiSo7
  )

dtStudents$viz$ProSocialBehaviorPt1 <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    ProSo1,
    ProSo2
  )

dtStudents$viz$ProSocialBehaviorPt2 <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    ProSo3,
    ProSo4
  )

dtStudents$viz$GoalsPt1 <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    StudentGoal01,
    StudentGoal02
  )

dtStudents$viz$GoalsPt2 <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    StudentGoal03,
    StudentGoal04
  )

dtStudents$viz$GoalsPt3 <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    StudentGoal05,
    StudentGoal06
  )

dtStudents$viz$GoalsPt4 <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    StudentGoal07,
    StudentGoal08
  )

dtStudents$viz$GoalsPt5 <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    StudentGoal09,
    StudentGoal10
  )

dtStudents$viz$SDT <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    Autonomy,
    Relatedness, 
    Competence
  )

dtStudents$viz$Attitudes <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    starts_with("Attitudes")
  )

dtStudents$viz$WB <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    ExWB
  )

dtStudents$viz$Event <- dtStudents$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    Event
  )

@@

```{r studentMeanViz, echo=FALSE, results='hide',fig.keep='all'} 
dtStudents$vizPlots <-
  lapply(seq_along(dtStudents$viz),
         function(i)
           meanVarPlot(dataIn = dtStudents$viz[[i]], 
                       name = names(dtStudents$viz)[[i]], 
                       namList = varNameListStudent))
dtStudents$vizPlots
```

@@

```{r medicalDataSelection}
varListMedical <- 
  c(
    "IntergroupContact",
    "InteractionDum",
    # "KeyNeedFulfillment",
    # "KeyNeedImp",
    "DaytimeNeedFullfillment",
    "DaytimeNeedImportance",
    "InteractionNeedFullfillment",
    "InteractionNeedImportance",
    "AntiSo1",
    "AntiSo2",
    "AntiSo3",
    "AntiSo4",
    "AntiSo5",
    "AntiSo6",
    "AntiSo7",
    "ProSo1",
    "ProSo2",
    "ProSo3",
    "ProSo4",
    "StudentGoal01",
    "StudentGoal02",
    "StudentGoal03",
    "StudentGoal04",
    "StudentGoal05",
    "StudentGoal06",
    "StudentGoal07",
    "StudentGoal08",
    "StudentGoal09",
    "StudentGoal10",
    "Autonomy",
    "Competence",
    # Break relatedness up into interaction vs. no interaction(?)
    # vars are already calculated
    "Relatedness",
    "AttitudesDutch",
    "AttitudesPartner",
    "exWB",
    "angry",
    "afraid",
    "energy",
    "lonelyAlways",
    "Event"
  )

varNameListMedical <- 
  c(
    "IntergroupContact" = "Dutch Interaction",
    "InteractionDum" = "Any Interaction",
    # "KeyNeedFulfillment" = "Key Need Fulfillment",
    # "KeyNeedImp" = "Key Need Importance",
    "DaytimeNeedFullfillment" = "Daytime Core Motive Fulfillment",
    "DaytimeNeedImportance" = "Daytime Core Motive Importance",
    "InteractionNeedFullfillment" = "Interaction Core Motive Fulfillment",
    "InteractionNeedImportance" = "Interaction Core Motive Importance",
    "AntiSo1" = "Put someone down",
    "AntiSo2" = "Show little attention in someones opinion",
    "AntiSo3" = "Demeaning remarks",
    "AntiSo4" = "Inpropperly addressing someone",
    "AntiSo5" = "Ignored or excluded someone",
    "AntiSo6" = "Doubt someones judgement",
    "AntiSo7" = "Unwanted attempts of personal matters",
    "ProSo1" = "Listen to someones problems",
    "ProSo2" = "Cheer someone up",
    "ProSo3" = "Help someone get things done",
    "ProSo4" = "Help someone with responsibilities",
    "StudentGoal01" = "Social support and connectedness",
    "StudentGoal02" = "Romantic or sexual relationship",
    "StudentGoal03" = "Academic",
    "StudentGoal04" = "Career",
    "StudentGoal05" = "Financial",
    "StudentGoal06" = "Health and fitness",
    "StudentGoal07" = "Leasure and fun",
    "StudentGoal08" = "Personal improvement and growth",
    "StudentGoal09" = "Service and help",
    "StudentGoal10" = "Spiritual or religious",
    "Autonomy" = "Autonomy",
    "Competence" = "Competence",
    # Break relatedness up into interaction vs. no interaction(?)
    # vars are already calculated
    "Relatedness" = "Relatedness",
    "AttitudesDutch" = "Outgroup Attitude",
    "AttitudesPartner" = "Attitude Interaction Partner",
    "exWB" = "Sadness Happiness",
    "angry" = "Anger",
    "afraid" = "Anxiety",
    "energy" = "Energy",
    "lonelyAlways" = "Loneliness",
    "Event" = "Positive or negative event present"
  )

@@

dtMedical$vizall <- dtMedical$full %>%
  select(
    PID,
    TID,
    TIDnum,
    all_of(varListMedical)
  )

dtMedical$viz$Interaction <- dtMedical$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    IntergroupContact,
    InteractionDum
  )

dtMedical$viz$KeyNeedFulfillment <- dtMedical$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    DaytimeNeedFullfillment,
    InteractionNeedFullfillment
  )

dtMedical$viz$KeyNeedImportance <- dtMedical$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    DaytimeNeedImportance,
    InteractionNeedImportance
  )

@@

@@

```{r medicalMeanViz, echo=FALSE, results='hide',fig.keep='all'} 
dtMedical$vizPlots <-
  lapply(seq_along(dtMedical$viz),
         function(i)
           meanVarPlot(dataIn = dtMedical$viz[[i]], 
                       name = names(dtMedical$viz)[[i]], 
                       namList = varNameListMedical))
dtMedical$vizPlots
```
